---
title: 'Homework #6'
author: "Connor Toliver; @connortoliver"
date: "4/20/2020"
output: html_document
---

# Top dogs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, let's load in our data and select what we want to use.

```{r}
library(tidyverse)
df <- readxl::read_xlsx('KIB - Best in Show (public).xlsx', sheet='Best in show full sheet', skip = 2)
df <- df %>% 
  select(breed = `Sources - see bottom right`, type = category, size = `size category`,
         score = `datadog score`, popularity = `POPULARITY IN US...6`, int = `INTELLIGENCE (TRAINABILITY) ranking`) %>% 
  na.omit()

head(df)
```

We have quitet a bit of cleaning to do. First, let's get rid of the first row because it's extraneous.


```{r}
df <- df[-1, ]

head(df)
```

Now, let's look at the structure of our data. 

```{r}
str(df)
```

`popularity` and `int` should be numeric. Let's change that. Let's also factor the size and change `int` to be more like the original graph.

```{r}
df$size <- factor(df$size, levels = c('small', 'medium', 'large'))
df$popularity <- as.numeric(df$popularity)
df$int <- as.numeric(df$int)

df <- df %>% 
  mutate(int = ifelse(int >= 0.5, 'clever', 'dumb'))
# x-axis: data score
# y-axis: popularity
# color: type
# size: size
# label: breed
# shape: intelligence
```

Now let's get started on the graphic with `ggplot`.

```{r}
ggplot(df, aes(x = score, y = popularity, color = type,
               size = size, shape = int)) +
  geom_jitter(alpha = 0.7) +
  ggrepel::geom_text_repel(aes(label = str_wrap(df$breed, width = 12)), size = ifelse(str_length(df$breed) > 15, 1.4, 1.8)) +
  geom_hline(yintercept = 77) +
  geom_vline(xintercept = 2.4) +
  xlim(min(df$score)-0.05, max(df$score)+0.5) +
  ylim(0, 200) +
  scale_y_reverse() +
  scale_size_discrete(range=c(3, 6, 9)) +
  theme_classic() +
  theme(legend.position='right', axis.text = element_blank(), axis.ticks = element_blank(),
        axis.line = element_blank()) +
  ggtitle('Best in Show: The Ultimate Data Dog') +
  xlab('Popularity') +
  ylab('Datadog Score') +
  labs(size = 'Size', color = 'Type', shape = 'Intelligence')
```

It's not exact, but it's a fairly reasonable reproduction of the original graph!